---
title: "EDI Analysis template"
author: "Luigi Neri"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## EDA

This is a file that I created following one blog. It want to be a template to perform an EDA analysis

Library that the lady loads are the following:

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidyquant)
library(modelr)
library(gridExtra)
library(grid)
```

In order to prepare the data the file is download from
this URL
"http://archive.ics.uci.edu/ml/machine-learning-databases/00352/Online%20Retail.xlsx"

I tried to save the file using download file but it does not quite work. The file apparently seem to be downloaded and saved but it has some problem when is opened. So I just download it and transform in a CSV using Excel. Then here below she uses a brilliant code for the processing. She can do that because it has few columns:


```{r eval=FALSE}
retail <- read_csv(f, col_types = cols
        (
         InvoiceNo = col_character(),
         StockCode = col_character(),
         Description = col_character(),
         Quantity = col_integer(),
         InvoiceDate = col_datetime("%d/%m/%Y %H:%M"),
         UnitPrice = col_double(),
         CustomerID = col_integer(),
         Country = col_character()
        )) %>% 
  mutate(day = parse_date(format(InvoiceDate, "%Y-%m-%d")),
         day_of_week = wday(day, label = TRUE),
         time = parse_time(format(InvoiceDate, "%H:%M")),
         month = format(InvoiceDate, "%m"),
         income = Quantity * UnitPrice,
         income_return = ifelse(Quantity > 0, "income", "return"))

```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
